### 2022-06-01 README.Rmd
update html version of manuscript
add mermaid graph to README

The most recent draft of the manuscript is available [here](https://brunalab.github.io/lagged-ipms/paper.html).

@@

-   Open the project in RStudio by double-clicking the `.Rproj` file.
-   This project uses `renv` for package management, which should be installed automatically when opening the project. Run `renv::restore()` to install all required packages.
-   Run `targets::tar_make()` or `targets::tar_make_clustermq()` from the R console to run all code and produce all outputs.

>>>>

The most recent draft of the manuscript is available [here](https://brunalab.github.io/lagged-ipms/docs/paper.html).

@@

-   Open the project in RStudio by double-clicking the `.Rproj` file.
-   This project uses `renv` for package management, which should be installed automatically when opening the project. Run `renv::restore()` to install all required packages.
-   This project uses `targets` for workflow management. The functions used in the project are defined in `R/` and the steps are defined in `_targets.R` and summarized in the schematic below. Run `targets::tar_make()` or `targets::tar_make_clustermq()` from the R console to run all code and produce all outputs.

```{r, echo=FALSE, message=FALSE, results='asis'}
cat(
  "```mermaid",
  targets::tar_mermaid(targets_only = TRUE),
  "```",
  sep = "\n"
)
#this should display correctly on GitHub, or code can be pasted into https://mermaid.live
```
